### 2024-10-01 manuscript/manuscript.qmd
docs(manuscript): correct graphViz figure

digraph sub {
  node [fontname = Helvetica, fontsize = 14, shape = box, width = 4]
  A [label = "Records identified from:
                Web of Science (n = 142)
                Scopus (n = 227)
                OpenALEX (n = 278)" ]
  B [label = "Records removed before screening: 
                Duplicates entries/errors (n = 94)" ]
  C [label = "Records after duplicates removed (n = 553)"]
  D [label = "Records screened (n = 553)"]
  E [label = "Records removed: 
                Irrelevant titles/themes (n = 338)
                Abstract screening (n = 95)
                Discussion (n = 24)"]
  F [label = "Full text articles assessed (n = 96)"]
  G [label = "Studies included in final review (n = 46)"]
  H [label = "Full text articles excluded
             (n = 50)"]
  I [label = "Studies excluded in final review (n = 8)"]
  J [label = "Final selection (n = 38)"]
  A->B
  A->C
  C->D
  D->E [ minlen = 3 ]
  D->F
  F->H [ minlen = 3 ]
  F->G
  G->I
  G->J

@@

| Concept      | Models, obs | $r$ \[95%-CI\]          | $t$   | $p$   | $\tau^2$ | $I^2$ |
|:---------|:---------|:------------|:---------|:---------|:---------|:---------|
| Valence All  | 120,73685   | 0.567 \[0.530; 0.603\]  | 23.7  | .0001 | 0.083    | 97.5% |
| Valence Max  | 24,15660    | 0.659 \[0.557; 0.740\]  | 10.14 | .0001 | 0.138    | 98.2% |
| *N Features* |             |                         |       |       |          |       |
| \<18 F       | 5,3036      | 0.811 \[0.566; 0.775\]  | \-    | \-    | 0.182    | 98.9% |
| 18-260 F     | 11,7318     | 0.548 \[0.343; 0.703\]  | \-    | \-    | 0.133    | 97.6% |
| 260+ F       | 7,4562      | 0.685 \[0.566; 0.775\]  | \-    | \-    | 0.044    | 97.2% |
| *Techniques* |             |                         |       |       |          |       |
| KS           | 2,2582      | 0.466 \[-0.634; 0.942\] | \-    | \-    | 0.0185   | 95.1% |
| LM           | 8,1762      | 0.784 \[0.625; 0.881\]  | \-    | \-    | 0.1370   | 96.4% |
| FD           | 6,4993      | 0.656 \[0.484; 0.779\]  | \-    | \-    | 0.0574   | 96.9% |
| NN           | 4,2249      | 0.340 \[-0.097; 0.668\] | \-    | \-    | 0.0761   | 97.1% |
| RF           | 4,4074      | 0.702 \[0.391; 0.869\]  | \-    | \-    | 0.057    | 98.5% |

>>>>

digraph sub {
  node [fontname = Helvetica, fontsize = 14, shape = box, width = 4]
  A [label = "Records identified from:
                Web of Science (n = 142)
                Scopus (n = 227)
                OpenALEX (n = 278)" ]
  B [label = "Records removed before screening: 
                Duplicates entries/errors (n = 94)" ]
  C [label = "Records after duplicates removed (n = 553)"]
  D [label = "Records screened (n = 553)"]
  E [label = "Records removed: 
                Irrelevant titles/themes (n = 338)
                Abstract screening (n = 95)
                Discussion (n = 24)"]
  F [label = "Full text articles assessed (n = 96)"]
  G [label = "Studies included in final review (n = 46)"]
  H [label = "Full text articles excluded
             (n = 50)"]
  I [label = "Studies excluded in final review (n = 9)"]
  J [label = "Final selection (n = 37)"]
  A->B
  A->C
  C->D
  D->E
  D->F
  F->H 
  F->G
  G->I
  G->J

@@

| Concept      | Models, obs | $r$ \[95%-CI\]          | $t$   | $p$   | $\tau^2$ | $I^2$ |
|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
| Valence All  | 120,73685   | 0.567 \[0.530; 0.603\]  | 23.7  | .0001 | 0.083    | 97.5% |
| Valence Max  | 24,15660    | 0.659 \[0.557; 0.740\]  | 10.14 | .0001 | 0.138    | 98.2% |
| *N Features* |             |                         |       |       |          |       |
| \<18 F       | 5,3036      | 0.811 \[0.566; 0.775\]  | \-    | \-    | 0.182    | 98.9% |
| 18-260 F     | 11,7318     | 0.548 \[0.343; 0.703\]  | \-    | \-    | 0.133    | 97.6% |
| 260+ F       | 7,4562      | 0.685 \[0.566; 0.775\]  | \-    | \-    | 0.044    | 97.2% |
| *Techniques* |             |                         |       |       |          |       |
| KS           | 2,2582      | 0.466 \[-0.634; 0.942\] | \-    | \-    | 0.0185   | 95.1% |
| LM           | 8,1762      | 0.784 \[0.625; 0.881\]  | \-    | \-    | 0.1370   | 96.4% |
| FD           | 6,4993      | 0.656 \[0.484; 0.779\]  | \-    | \-    | 0.0574   | 96.9% |
| NN           | 4,2249      | 0.340 \[-0.097; 0.668\] | \-    | \-    | 0.0761   | 97.1% |
| RF           | 4,4074      | 0.702 \[0.391; 0.869\]  | \-    | \-    | 0.057    | 98.5% |
